Truthfulness Verification System

### 2011-05-04 trunk/proposal/paper.tex
fixed url

\paragraph{Example}

A description of the above steps applied to the five problematic sentences
\begin{enumerate}
\item Sentence 1: Les Paul invented the electric guitar.
\begin{enumerate}
\item AU: Les\_Paul, Gibson Les, Leo, Llyod, Adolph Rickenbacker. 
\item Wiki articles detected from AU($W_{au_{i}}$): Les\_Paul, Leo (disambiguation page), Adolph\_Rickenbacker 
\item Wiki articles detected from TU($W_{tu_{i}}$): The\_guitar, The\_Electric\_guitar, Electric\_guitar, invented Invention 
\end{enumerate}

\item Sentence 2: Tom Hanks is the lead actress of the movie Sleepless in Sattle.
\begin{enumerate}
\item AU: hanks meg, meg ryan, tom hanks, nora, sam
\item Wiki articles detected from AU($W_{au_{i}}$): Meg\_Ryan, Tom\_Hanks, Nora(Disambiguation), Sam(Disambiguation page) 
\item Wiki articles detected from TU($W_{tu_{i}}$): Sleepless\_in\_Seattle, Lead, Lead-in, Leading\_actor(automatically redirected from Leading actress), Movie(automatically redirected from Film), Sleepless(disambiguation page), Seattle(lands on the correct page, though there is a disambiguation page).
\end{enumerate}

\item Sentence 3: Apollo was the first spacecraft on the moon.
\begin{enumerate}
\item AU: apollo, land, landing, luna
\item Wiki articles detected from AU($W_{au_{i}}$): Apollo, Land(disambiguation page), Landing(disambiguation page), Luna(disambiguation)
\item Wiki articles detected from TU($W_{tu_{i}}$): Fisrt(disambiguation page), Moon, Spacecraft.
\end{enumerate}

\item Sentence 4: english is the primary language of the philippines.
\begin{enumerate}
\item AU: english, filipino, spansih, education, history
\item Wiki articles detected from AU($W_{au_{i}}$): English disambiguation page), Filipino(disambiguation page), Spanish(disambiguation), Education, History
\item Wiki articles detected from TU($W_{tu_{i}}$): Primary (disambiguation page), language(disambiguation page), First\_Language (automatically redirected from Primary Languge), Philippines.

\end{enumerate}

\item Sentence 5: Michael Phelps is the fastest swimmer in the world
\begin{enumerate}
\item AU: michael, long, ernest, sullivan, alexander
\item Wiki articles detected from AU($W_{au_{i}}$): Michael, Alexander, Sullivan(disambiguation page), Long(disambiguation page), Ernest(disambiguation page) 
\item Wiki articles detected from TU($W_{tu_{i}}$): Fastest, Swimming(sport) (automatically redirected from Swimmer),World.

\end{enumerate}

\end{enumerate}

Please refer to the hand out analysis of the results.

@@

\paragraph{Examples}
Detail working of Sentence Structure (Algorithm 2) is described for following sentence is given below:

@@

For this sentence the alternative units are les paul, gibson les, llyod, leo, adolph rickenbacker. The top wikipedia page from google search is http://en.wikipedia.org/wiki/Electric\_guitar. So we download this page. Convert it to text from html and split into sentences. Then we match each alternate unit with all the sentences to see if there is any intersection with the alternate unit. We found intersection for the alternate units les paul, gibson les, llyod, and adolph rickenbaker but not for leo. Hence leo get a score of zero and we process other alternative units further. In the next step, we find intersection between content words or topic unit and matched sentences for alternate units found in the previous step. We count no of words that are overlapped and rank alternate units according to this count value. Count of the content word overlap is given below.

@@

 It shows that we have 3 content word intersection for les paul, 1 word intersection for gibson les and 0 for all other alternate units. This ranking is the final truth or confidence ranking for all alternate units

>>>>

\paragraph{Example}
Detail working of Bag of Words (Algorithm 1) for following sentence is given below:

For this sentence, the alternative units are les paul, gibson les, llyod, leo, adolph rickenbacker. At first, we generate all possible k-grams from the topic unit. The generated k-grams are following:

['invented', 'Invented', 'invented the', 'Invented The', 'invented the electric', 'Invented The Electric', 'invented the electric guitar', 'Invented The Electric Guitar', 'the', 'The', 'the electric', 'The Electric', 'the electric guitar', 'The Electric Guitar', 'electric', 'Electric', 'electric guitar', 'Electric Guitar', 'guitar', 'Guitar']

Now for each k-gram we find relevant wikipedia page. We will not get any wikipedia page for irrelevant k-gram combination.  Moreover, We may get a page directly or we may need to disambiguate. Following are the all relevant pages. The False in the second column page there is no ambiguation and True means we need to disambiguate.

\url{http://en.wikipedia.org/wiki/Invention}, False\\
\url{http://en.wikipedia.org/wiki/The_Electric}, True \\
\url{http://en.wikipedia.org/wiki/Electric_guitar}, False\\
\url{http://en.wikipedia.org/wiki/Electricity}, False \\
\url{http://en.wikipedia.org/wiki/Electric_guitar}, False \\
\url{http://en.wikipedia.org/wiki/Guitar}, False

For the above pages, we need to disambiguate for one page only and that is \url{http://en.wikipedia.org/wiki/The_Electric}. We described earlier that we look into the count of overlap between topic unit words and disambiguation link description words. For this disambiguation there is no overlap and so we do not need to process this page further. Hence the final set of $n$ pages are following:

\url{http://en.wikipedia.org/wiki/Invention} \\
\url{http://en.wikipedia.org/wiki/Electric_guitar} \\
\url{http://en.wikipedia.org/wiki/Electricity} \\
\url{http://en.wikipedia.org/wiki/Electric_guitar} \\
\url{http://en.wikipedia.org/wiki/Guitar}

In the next step, we find relevant Wikipedia page for each of the alternate units. There are no relevant Wikipedia page for  gibson les and llyod. Hence we do not process these alternative units further. For the remaining three alternative units, there is no ambiguation for les paul and adolph rickenbacker. The corresponding pages are following:

\url{http://en.wikipedia.org/wiki/Les_Paul}\\
\url{http://en.wikipedia.org/wiki/Adolph_Rickenbacker}

However we need to disambiguate for the page corresponding to Leo:

\url{http://en.wikipedia.org/wiki/Leo}

After disambiguation for Leo using word overlap between description and topic unit words, we get following page:

\url{http://en.wikipedia.org/w/index.php?action=raw&title=Leo_(constellation)}

Now, we need to count word overlap for each of the pages for les paul, adolph rickenbacker, leo with all pages for the topic unit and take sum of the overlap to produce the ranking of alternate units

%A description of the above steps applied to the five problematic sentences
%\begin{enumerate}
%\item Sentence 1: Les Paul invented the electric guitar.
%\begin{enumerate}
%\item AU: Les\_Paul, Gibson Les, Leo, Llyod, Adolph Rickenbacker. 
%\item Wiki articles detected from AU($W_{au_{i}}$): Les\_Paul, Leo (disambiguation page), Adolph\_Rickenbacker 
%\item Wiki articles detected from TU($W_{tu_{i}}$): The\_guitar, The\_Electric\_guitar, Electric\_guitar, invented Invention 
%\end{enumerate}
%
%
%
%\item Sentence 2: Tom Hanks is the lead actress of the movie Sleepless in Sattle.
%\begin{enumerate}
%\item AU: hanks meg, meg ryan, tom hanks, nora, sam
%\item Wiki articles detected from AU($W_{au_{i}}$): Meg\_Ryan, Tom\_Hanks, Nora(Disambiguation), Sam(Disambiguation page) 
%\item Wiki articles detected from TU($W_{tu_{i}}$): Sleepless\_in\_Seattle, Lead, Lead-in, Leading\_actor(automatically redirected from Leading actress), Movie(automatically redirected from Film), Sleepless(disambiguation page), Seattle(lands on the correct page, though there is a disambiguation page).
%\end{enumerate}
%
%\item Sentence 3: Apollo was the first spacecraft on the moon.
%\begin{enumerate}
%\item AU: apollo, land, landing, luna
%\item Wiki articles detected from AU($W_{au_{i}}$): Apollo, Land(disambiguation page), Landing(disambiguation page), Luna(disambiguation)
%\item Wiki articles detected from TU($W_{tu_{i}}$): Fisrt(disambiguation page), Moon, Spacecraft.
%\end{enumerate}
%
%\item Sentence 4: english is the primary language of the philippines.
%\begin{enumerate}
%\item AU: english, filipino, spansih, education, history
%\item Wiki articles detected from AU($W_{au_{i}}$): English disambiguation page), Filipino(disambiguation page), Spanish(disambiguation), Education, History
%\item Wiki articles detected from TU($W_{tu_{i}}$): Primary (disambiguation page), language(disambiguation page), First\_Language (automatically redirected from Primary Languge), Philippines.
%
%\end{enumerate}
%
%
%\item Sentence 5: Michael Phelps is the fastest swimmer in the world
%\begin{enumerate}
%\item AU: michael, long, ernest, sullivan, alexander
%\item Wiki articles detected from AU($W_{au_{i}}$): Michael, Alexander, Sullivan(disambiguation page), Long(disambiguation page), Ernest(disambiguation page) 
%\item Wiki articles detected from TU($W_{tu_{i}}$): Fastest, Swimming(sport) (automatically redirected from Swimmer),World.
%
%\end{enumerate}
%
%
%\end{enumerate}
%
%Please refer to the hand out analysis of the results.

@@

\paragraph{Examples}
Detail working of Sentence Structure (Algorithm 2) for following sentence is given below:

@@

For this sentence the alternative units are les paul, gibson les, llyod, leo, adolph rickenbacker. The top wikipedia page from google search is \url{http://en.wikipedia.org/wiki/Electric_guitar}. So we download this page. Convert it to text from html and split into sentences. Then we match each alternate unit with all the sentences to see if there is any intersection with the alternate unit. We found intersection for the alternate units les paul, gibson les, llyod, and adolph rickenbaker but not for leo. Hence leo get a score of zero and we process other alternative units further. In the next step, we find intersection between content words or topic unit and matched sentences for alternate units found in the previous step. We count no of words that are overlapped and rank alternate units according to this count value. Count of the content word overlap is given below.

@@

 It shows that we have 3 content word intersection for les paul, 1 word intersection for gibson les and 0 for all other alternate units. This ranking is the final truth or confidence ranking for all alternate units.
